\chapter{The ATLAS Detector} \label{chap:atlas}

Given the immense energies availalbe at the LHC, and the veritable zoo of
paricles we are trying to detect, we require a general-purpose experiment in
order to fully exploit the full range of physics opportunities provided.  Two
international collaborations rose to this challenge, the CMS (Compact Muon
Solenoid) and ATLAS (A Torroidal LHC ApparatuS) experiments.  While both have
similar physics goals and each of them strengths and weaknesses, this
dissertation will focus on the ATLAS experiment and the intricacies of its three
main sub-detectors and two massive magnet systems.  

Located approximately 100 meters underground in a vast excavated chamber, the
ATLAS detector rests its 7000 metric tonnes on a bed of concrete reinforced
steel.  Out of it flows the signals of over 100 million electronic channels
through a zip tied mass of greater than 3000 kilometers of cabling.  At its very
center is one of the four interaction points of the LHC, specifically Point 1,
where the two counter circulating proton beams are skillfully shaped and then
collided by a series of magnets.  The energetic particles resultant from this
collision then fly out in all directions into the bulk of the ATLAS detector.

The first sub-system they meet is the Inner Detector (ID) and its many layers of
strip and pixel silcon detectors along with a transition radiation gaseous wire
detector, all bathed in the 2T mangnetic field of the surronding superconducting
solenoidal magnet.  This system exploits the ionization of charged particles to
track their curved trajectory through the magnetic field.  This curvature gives
us charge information, a momentum measurement, and precision 3D verticies
crucial to the identification of the secondary verticies of a b-hadron decay. 

Outside of the solenoid the particles are faced with first the Electromagnetic
and then the Hadronic sampling calorimeters. Here, layers of scintillator and 
high radiation length materials are implemented to measure the energy of
electrons, photons, and hadrons.  The goal being to absorb all of the energy of
the partilces in order to have an accurate measurement.

Finally we have the muon system surrounding the calorimeter and equipped with
its own torroidal magnet system.  Here the charged muon bends in the magnetic
field while leaving a trail of ionization in the muon spectrometer before
exiting the detector completely.  Neutrinos are the only other standard model
particle that leave the detector, however they do so without detection.

In the following sections I will explain our choosen coordinate system and give 
a more detailed reveiw of these 3 detector sub-systems.  

\input{chapters/atlas/coordinates.tex} 
\input{chapters/atlas/tracking.tex} 
\input{chapters/atlas/calorimetry.tex}
\input{chapters/atlas/muons.tex}
