\label{sec:acknowledgements}

There is no way I can fully express my gratitude for the people and places that
have made this journey all that it has been.  The path to this degree has been
winding, uncertain and full of mistakes.  The names below represent a small
sample of the rich bounty this life has offered me for guidance and support. I
am eternally grateful to them all.

Thank you Jason Nielsen for personally calling me and inviting me to work with
you nearly seven years ago.  I didn't know how lucky I was back then, but I can
definitively say now I wouldn't have it any other way.  Your patience,
exuberance, curiosity and kindness have taught me the power of questions and
the boundless possibilities of an inquisitive mind. Thank you for these gifts,
and for supporting me in the pursuit of my dreams.

Thank you to my committee members, Michael Hance and Abraham Seiden, for
bearing with the hectic timeline this dissertation was created on.  You
supported my less than traditional writing style and have helped me produce a
document  my family and I can be proud of for years to come.

Thank you to my collaborators in ATLAS and all my individual analysis groups.
It has been an incredible honor to work with such a diverse and devoted group
of brilliant scientists.  Our incredible success as a field stands as a
testament to the ingenuity and determination that can only come from
cooperation.  Particle physicists have shown me what a world without boarders
looks like, and I am grateful to count myself amongst their ranks.

Thank you to the teachers and professors who helped me realize my dream of
becoming a scientist and more: Richard Toothman, John McDaniel (McD), Kelley
Molitor, Mani Tripathi, Manuel Calder\'on de la Barca S\'anchez, Randy Harris,
and Joel Primack.  You believed in me and I will never forget the power of that
gift.

Thank you to Giordon Stark for seeing my potential and setting me on the path
to policy.  You have been a solid shoulder to lean on, a kind ear (eye?) to my
worries and a powerful mind to sharpen my own against. Your friendship and
brilliance make this world more friendly and interesting, everywhere you go.
Also your baking is so good it should come with a warning label.

Thank you to the many post doctoral students at UCSC who have pulled me out of
the academic mud time and time again: Matthew, Andrea, Simone, Hass, Chiara and
Ryan.  Navigating the ATLAS collaboration without your guidance and protection
seems an impossible task, we are all in your debt.

Thank you to my physics cohort for all the late night homework sessions and
your continuing friendship and support: Joey, Max, Ross, Dean, Cam, Mike, Dave,
Noah, Peizei, Ahram, Skyler, Christoph, Eudald, Daniel, Philip.  You're all
brilliant and I can't wait to see where life takes you all. 

Thank you to the UCSC graduate students who helped me along the way, sometimes
with words of encouragement, other times with a stiff drink but always with a
smile: Sheena, Peyton, Eric, Jeff, Alexander, Monika, Carey, Doug, Brian,
Muiris, Daniel, Jerah, Katie, Tayler, Daniel, Zippy, Carolyn, Cole, Natasha and
many more.  Graduate school is hard in a way very few people can understand,
I'm so glad I didn't have to travel this path alone, thanks to you.

Thank you to my Santa Cruz housemates through the years: Elizabeth, Tessa,
Stas, Dave, David, Rob, Roy, Zad, Brent, Philip, Graham, Kelly and Catherine.
The house on Laurel Street will always be a special place in my memories and my
heart.  The music, food, dance and discussion we shared have taught me what
true community looks like.  My love and gratitude to all of you, I couldn't ask
for better or more supportive friends.

Thank you to the Santa Cruz locals for all the shenanigans and
memories: Cleveland, Gabe, Monica, Travis, Saul, Bob, Larry, Deidre, Brian,
Philip, Sean, Lance, Chappy, Keelin, Angelica, Kage, Mikey (thanks for the
laundry), Michael, Micha, Xander, Gabriel, Julian, Brooke, Maya, Rafferty,
Allie, Sam, Kate, Carrie, Alex, Cesar, Nora, Chris and many more. Our time
together gave me the moments of rest and relaxation I needed to keep me sane.

Thank you to my Geneva housemates during my time in Switzerland: Rob, Bijan,
Leigh and Jennifer.  Living abroad was scary and hard until you welcomed me
into the Marigold Memory Palace and your hearts.  Here's to the future and our
continued friendship. 

Thank you to everyone who made my time living abroad an exciting and eye
opening experience: Fenton, Paolo, Ivan, Marika, Niko, Oliver, Ranveig,
Tristan, Apostolos, Efi, Irene, Leo, Arizona, Soph, Elsa, Adrian, George,
Kelvin, Dayane, Enrica, Sam, Galen, Kisa, Babette, Viktoria, Adam, Sam, Joel,
Amal, Danii, Flavia, Julie, Cameron, Mor, Swathi, Gabriella (Biscoitinha),
Duncan, Eddie, Murdo, Lewis, Stoyan, Sophie, Sun, Xanthe, the entire LTA,  and
many more.  Together we danced, hiked, boxed, ran, snowboarded, flew, sailed,
biked and rode our way through more adventures than I'd ever thought possible.
My life is so much richer thanks to you.

Thank you to Josh and Emmanuel for putting up with having a crazy particle
physicist as the intern for 10 weeks.  You gave me the foot in the door I
needed to set off on the next stage of my life in policy.  Next round of coffee
is on me.

Thank you to Heidi for being there for me in what has been the most trying
period of my life thus far.  You saw me through Giardia, injuries and crippling
writing stress.  Whatever life brings us, I am lucky to have had your strength
during this time. 

Thank you to Vin for seeing me through the lowest lows and the highest highs.
You've done more for me than words can describe.  I treasure your friendship
and will always love you.  Here's to our next adventure!

Thank you to my sister Yara for being my best friend.  I can talk to you about
anything, from group theory to relationships to politics and always appreciate
your advice.  I can't wait to see what you do in this world and am thankful to
have you in my life, love you moo moo.

Thank you to my parents Mike and Izzy.  You gave me life, you fostered my
imagination, and have bent over backwards to support my dreams.  All of my
accomplishments, all of my life, I owe in some part to you and your example. My
love and gratitude towards you knows no bounds and will exist as long as I'm
living.

Thank you to music for giving me a way to express myself when nothing made
sense.  In my times of greatest need I have found strength in your ethereal
arms. A special thanks to the local Irish session, all my Lark friends and
Nathaniel Berman and his concert choir and wind ensemble.

Thank you to science for giving me the tools to answer my never ending
questions.  You have given me the lens I needed to make sense of this world,
and my what a beautiful world it is. 

And finally, thank you to the Earth for giving us such a beautiful, bountiful
and rich place to call home.
