\chapter{The Standard Model and Beyond} \label{chap:standard_model}

The Standard Model (SM) of Particle Physics formalizes the force laws that
describe the observed behavior of all known particles in the universe. Its
formulation is a collection of Quantum Field Theories (QFT) that describe the
following interactions of elementary matter in Nature: the electromagnetic
force, the weak nuclear force and the strong nuclear force.  Gravity is
noticeably absent as currently there is no viable quantum theory for observed
gravitational effects.  The Glashow-Salam-Weinberg (GSW) \cite{Glashow:1961tr,
Salam:1968, Weinberg:1967tq} theory includes Quantum ElectroDynamics
(QED) and describes the unification of the electromagnetic and weak forces,
while Quantum ChromoDyanmics (QCD) \cite{Campbell:2017hsr} describes the strong
force.  These theories form the following symmetry group of the Standard Model:

\begin{equation} \label{eq:standardmodel:symmetry_group}
  \underbrace{\text{SU}_\text{C}(3)}_\text{QCD} \otimes
\underbrace{\text{SU}_\text{L}(2) \otimes \text{U}_\text{Y}(1)}_\text{GSW}.
\end{equation}

The gauge principle states that the SM Lagrangian and its predictions must be
invariant under local transformations using an operator from any of these
constituent groups.  Thus, any theory must only include transformations and
terms that maintain the local invariance of the complete Lagrangian.  In
particular, this requirement is violated by any attempt to include an explicit
mass term for the gauge bosons of the GSW electroweak model and for all
fermions.  Around 1960 a possible solution to this lack of mass was proposed in
the form of the spontaneous breaking of the electroweak symmetry, now known as
the Higgs mechanism.  The following sections go into more detail about the
Lagrangian formalism of the Standard Model, QCD, GSW electroweak unification
and this recently verified Higgs mechanism.

\input{chapters/theory/standardmodel.tex}
\input{chapters/theory/gsw.tex}
\input{chapters/theory/qcd.tex}
\input{chapters/theory/higgs.tex}
