\section{Selected Triggers} \label{sec:selection:triggers}

This analysis uses exclusively large-$R$ jet triggers in order to maximally
capture the boosted decay products of the Higgs boson. However, pile-up
increased over the course of LHC Run 2 as shown in \Cref{fig:pileup}. This
increase in pile-up corresponds to an increase in the underlying event energy
that can be clustered into jets and thus an increase in the rate of the
large-$R$ jet trigger. As a result the High Level Trigger (HLT) $\pT$
requirement was increased over the years in order to maintain a low trigger
rate for data recording.  This results in a different triggering algorithm for
the 2015, 2016, and 2017 data taking years.  While all the triggers require a
large-$R$ jet to be reconstructed in the HLT, the 2015 and 2016 triggers used
an ungroomed (a10) large-$R$ jet algorithm while in 2017 a trimmed (a10t)
version was used.  In 2015 the large-$R$ trigger looked for an ungroomed
large-$R$ jet with $\pT > 360~\GeV$.  In 2016 the $\pT$ threshold was raised to
$420~\GeV$.  In 2017 the requirement changed to look for a trimmed large-$R$
jet with $\pT > 480~\GeV$.  This information is summarized in
\Cref{table:triggers}, which also details the integrated luminosity for the
various triggers as well as the offline $\pT$ threshold.  In all cases the
offline threshold differs from the HLT threshold.  This is due to the fact that
the trigger must make a quick calculation of the jet energy in order to keep
data rates low. However, this online calculation sacrifices accuracy, so some
jets that should have passed are instead ignored.  This results in a turn-on
curve in the $\pT$ distribution near the online threshold where the trigger is
not yet fully efficient. Thus, a higher offline threshold is chosen
corresponding to when the trigger is fully efficient.  All triggers used in
this analysis are fully efficient for an offline threshold of $\pT > 480~\GeV$.
In order make sure the triggers are fully efficient in the offline selection,
all events are required to contain a trimmed large-$R$ jet with $\pT >
480~\GeV$.

\begin{table}[htpb]
 \centering 
  \caption{ Summary of the large-$R$ jet triggers used for the data taking
periods of 2015, 2016, and 2017 and the offline $\pT$ thresholds at which
they become fully efficient. The recorded integrated luminosity for each
trigger is also included \cite{Krizka:2310645}.}
 \begin{tabular}{@{}rlrr@{}}
  \toprule
  Year   & Trigger Name                 & Offline $\pT$ Threshold~$(\GeV)$ & Luminosity~$\left(\ifb\right)$ \\ \midrule
  $2015$ & $\text{HLT\_j360\_a10\_lcw\_sub\_L1J100}$  & $410$                              & $3.2$                          \\
  $2016$ & $\text{HLT\_j420\_a10\_lcw\_L1J100}$      & $450$                              & $33.0$                         \\
  $2017$ & $\text{HLT\_j460\_a10t\_lcw\_jes\_L1J100}$ & $480$                              & $44.3$                         \\
  \bottomrule
 \end{tabular}
 \label{table:triggers}
\end{table}
