\section{Signal Monte Carlo} \label{sec:data:signal_mc}

In order to simulate Higgs events the three leading production mechanisms at
the LHC were considered, shown in \Cref{fig:higgs_production}: gluon-gluon
fusion, vector boson fusion and Higgstralungh.  These three production modes
correspondingly represent 50\%, 30\% and 20\% of the total Higgs signal before
analysis cuts are applied.  In all samples the simulated Higgs is decayed to
the $b\bar{b}$ final state our analysis focused on.

The ggF plus an associated jet events were generated using the
HJ+MiNLO~\cite{Hamilton2015} prescription, assuming a finite top quark mass,
with the \textsc{Powheg-Box}~\cite{Campbell2012} 2 generator and the NNPDF30
NNLO~\cite{Hamilton:2012rf} parton distribution function.  After generation the
events are showered using \textsc{Pythia} 8.212~\cite{Sjostrand:2014zea} with
the AZNLO tune and the CTEQ6L1~\cite{Pumplin:2002vw} parton distribution
function. Any $b$-hadrons produced during this process are decayed using
\textsc{EvtGen}~\cite{LANGE2001152}.

The VBF Higgs events also generated using the
\textsc{Powheg-Box}~\cite{Nason:2009ai} generator with the NNPDF30
NLO~\cite{Hamilton:2012rf} parton distribution function. Again the showering is
performed with \textsc{Pythia} 8.212~\cite{Sjostrand:2014zea} using the AZNLO
tune and the CTEQ6L1~\cite{Pumplin:2002vw} parton distribution function.  The
decay of $b$-hadrons is again performed using
\textsc{EvtGen}~\cite{LANGE2001152}.

Higgstralung events were generated using the \textsc{Pythia}
8.212~\cite{Sjostrand:2014zea} generator, the AZNLO tune and the
CTEQ6L1~\cite{Pumplin:2002vw} parton distribution function.  Again the decay of
$b$-hadrons is handled by \textsc{EvtGen}~\cite{LANGE2001152}. Unfortunately
the \textsc{Pythia} process doesn't include the $gg \rightarrow ZH$
contribution.  To account for this we corrected the cross section to the LHC
Higgs cross section working group's (LHCHXSWG) recommendation
\cite{MelladoGarcia:2150771}.
